---
title: "Assignment 17"
author: "Achdiyat Kusuma"
date: "4/27/2021"
output: html_document
---

```{r}
library(tidyverse) # data manipulation
library(cluster) # clustering algorithms
library(factoextra)
library(gridExtra)
setwd("C:/Users/user/Desktop/KURSUS/DATA SETS")
getwd()
mov <- read.csv('customer_movie_rating.csv')
head(mov)
```

```{r}
mov <- na.omit(mov)
mov <- scale(mov)
head(mov)
```

```{r}
k <- kmeans(mov, centers = 5, nstart = 25)
str(k)
```

```{r}
fviz_cluster(k, data = mov)
```

```{r}
mov %>%
as_tibble() %>%
mutate(cluster = k$cluster,
state = row.names(mov)) %>%
ggplot(aes(Horror, Romcom, Action, Comedy, Fantasy, color =
factor(cluster), label = state)) +
geom_text()
```

```{r}
k2 <- kmeans(mov, centers = 2, nstart = 25)
k3 <- kmeans(mov, centers = 3, nstart = 25)
k4 <- kmeans(mov, centers = 4, nstart = 25)
# plots to compare
p2 <- fviz_cluster(k2, geom = "point", data = mov) + ggtitle("k = 2")
p3 <- fviz_cluster(k3, geom = "point", data = mov) + ggtitle("k = 3")
p4 <- fviz_cluster(k4, geom = "point", data = mov) + ggtitle("k = 4")
p5 <- fviz_cluster(k, geom = "point", data = mov) + ggtitle("k = 5")
library(gridExtra)
grid.arrange(p2, p3, p4, p5, nrow = 2)
```

```{r}
set.seed(123)
fviz_nbclust(mov, kmeans, method = "wss")
```
```{r}
set.seed(123)
fviz_nbclust(mov, kmeans, method =
"silhouette")
```
#K2 Distributed the data into 2 Clusters with no collision with each of the data. This one is also what is considered the best Number of clusters by using elbow and silhoutte methods

#K3 Even though there are no Collision of data, this one is considered not as effective

#K4 While there is one cluster that remains the same, the other clusters have too much data that collide with each other and it become hard to see

#K5 Even though it supposedly represent each variable of the data, the graph become even more crowded on the left side and is now even harder to see


# Conclusion : From the data above, we can plainly see that as suggested by the using the elbow and silhoutte graph the best K-means for this data is K2 (the ones with 2 clusters). The K2 graph can be easily understood as it divides the data into 2 major cluster with no collision with each data.

